Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
updates to experimental section

We applied HSLDA, along with three other closely related models, to
the clinical data and the retail product data. Specifically, we evaluate
models including sLDA with independent regressors (hierarchical constraints
on labels ignored), HSLDA fit by performing LDA followed by tree-conditional
regressions, and HSLDA fit with fixed random regression parameters. These
models were chosen to highlight several aspects of the model including performance in the absence 
of hierarchical constraints, the effect of the combined inference procedure, and regression
performance attributable solely to the hierarchical constraints.

We evaluated model performance for all three models with a range of
values for $\mu$ ($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\} )$,
the mean prior parameter for regression parameters.

\subsection{Evaluation}

%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}

The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first evaluation method augments the
observed labels in the held out set with their ancestors and considers
all other non-existant labels to be negative. The second method ignores
the ancestors of the observed labels in the held out set and considers
all other non-existant labels to be negative. This uniform treatment
of ancestors allows for a fair comparison of the models.

The two measures for predictive performance used here include the
true positive rate and the false positive rate evaluated based on
$p\left(y_{l,\hat{d}}\mid w_{1:N,d}\right)$ for each label in each
model.

>>>>

We evaluated HSLDA along with three other closely related models against 
these two datasets. The comparison models included sLDA with independent 
regressors (hierarchical constraints on labels ignored), HSLDA fit by 
performing LDA followed by tree-conditional regressions, and HSLDA fit 
with fixed random regression parameters. These models were chosen to 
highlight several aspects of the model including performance in the absence 
of hierarchical constraints, the effect of the combined inference procedure, and regression
performance attributable solely to the hierarchical constraints.

sLDA with independent regressors is the most salient comparison model
for our work. The distinguishing factor between HSLDA and sLDA is the
addition structure imposed on the label space, a distinction that we
hypothesize will result in a difference in predictive performance. 
Aside from this, all other features of sLDA are preserved between the two models.

There are two components to HSLDA, LDA and a hierarchically constrained response.
The second comparison model is HSLDA fit by performing LDA first followed by
performing inference over the hierarchically constrained label space. In this
comparison model, the separate inference processes do not allow the responses
to influence the low dimensional structure inferred by LDA. Combined inference
has been shown to improve performance in sLDA \citep{BleiMcAuliffe2008}. This
comparison model examines not the structuring of the label space, but the benefit
of combined inference over both the documents and the label space.

The last comparison model is HSLDA with fixed and randomly selected regression
parameters. There is a baseline benefit that the structure in the label space 
provides for the prediction of labels. This comparison model is intended to
quantify the contribution of the structure alone.

We evaluated model performance for all three models with a range of
values for $\mu$, the mean prior parameter for regression parameters 
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$). The number of topics for all
models was set to 50, the parameters for the prior distributions
$\alpha$, $\alpha^prime$, and $\gamma$ were a shape parameter of 1
and a scale parameters of 1000.

\subsection{Evaluation and Results}

%Outline:
%1. Model evaluation goal, metrics
%2. Gold standard(s), properties
%3. Method for prediction w/ details
%4. Discussion of results
%5. Connection of results with contribution and generality etc

We evaluated our model, HSLDA, against the comparison models with a focus
on predictive performance. Predictive performance was measured with
standard metrics of performance - sensitiviy (true positive rate) and 
1-specificity (false positive rate). We evaluate on the two aforementioned
datasets to demonstrate that model performance generalizes over two very disparate
domains.

To evaluate the performance of these models, we establish a gold standard for comparison.
In our evaluation of each dataset, a held out set of 1000 documents and labels were
reserved for evaluation and predictive performance was evaluated against the observed
labeling. Specifically, ancestors of observed nodes were ignored, observed nodes 
were considered positive and unobserved nodes were considered to be negative. The gold
standard defined in this way will likely lead to a slight overestimation of the number of
false positives. It is known that ICD-9 codes lack sensitivity and their use as a
gold standard could lead to correctly positive predictions being labeled as false positives.
However, given that the label space is often large (as in our examples) these potentially
erroneous false positives should not skew results significantly.

Predictive performance in HSLDA is evaluated by $p\left(y_{l,\hat{d}}\mid w_{1:N_{\hat{d}},\hat{d}}, w_{1:N_d,1:D},  y_{l\in\mathcal{L},1:D}\right)$ where $\hat{d}$ represents the test document. For efficiency,
the expectation of this probability distribution was estimated in the following way. Expectations
of $\mathbf{\bar{z}}_d$ and $\boldsymbol{\eta}_l$ were estimated with samples from the posterior.
Using these expectations, we performed Gibbs sampling over the hierarchy to acquire predictive
samples for the documents in the test set.
